Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-28 doc/main_jfm.tex
working on numerical results

\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
We begin by studying the dynamics of a single Janus-vesicle suspended in
the shear flow
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_2) \mathbf{e}_1,
\end{align}
with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_1$
and $\mathbf{e}_2$ for the horizontal and vertical directions
respectively. It is well known that a vesicle has tank-treading behavior
when there is no viscosity contrast between the fluids inside and
outside of the vesicle.
%Within the framework of the simulation setup,
%the proposed model provides a feature that the fluid viscosity is
%constant over the computational domain and it is capable of performing
%these simulations.

@@

\subsubsection{Intermonolayer friction}
An interesting phenomenon also rises up in the proposed setup where the inter-monolayer slip occurs 
between two leaflets. When a shear rate is large enough, take $\chi = 0.005$ as an example, 
Figure~\ref{figure5} shows the schematic of the test where a particle pair is initially marked and we then track the positions of this particle pair over a period of time. 
In this series of tests, we monitor the mean particle position change and mean angle $\theta(t)$ between particle relative positions with respect to the vesicle center over the time. It is clear to see that the outer leaflet always has larger tangential velocity than the one from the inner leaflet and the mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon is consistent with what has been seen
in articles in molecular dynamics simulations.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{The schematic of the intermonolayer slip over a period of time. Taking shear rate $\chi=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=2000$ and $t=9000$. The midplane curve is denoted as $\Sigma_M$. We provide numerical results of $\theta(t)$ for cases of shear rates $\chi$.
  }
    \label{figure5}
\end{figure}

To calculate the inter-monolayer friction coefficient for the apposing JP leaflets, we let  
\begin{equation}
b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle },
\end{equation}
%
where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot \sigma \cdot \nnu} \,ds\rangle$ 
is the time-averaged, tangential force along the midplane curve $\mathcal{C}_m$. 
The parameters $\langle L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve length and
intermonolayer slip velocity respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}

Besides the tests of a Janus-vesicle in a shear flow, an interesting test can also use the proposed model and the setup. Consider a symmetric parabolic flow about the $x$-axis, \cite{Kaoui09} studied shapes of the red blood cell immersed in a parabolic flow using a continuum model. With a similar setup, the background flow for this set of simulations is given by
\begin{equation}
\uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.

Figure~\ref{figure6} gives three configurations for one specific case where the centroid of the Janus-vesicle is initially placed slightly above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and $R_0=8$. The red curves are the midplanes and a particle pair is marked in color. We observe that the deformed 
Janus-vesicle has a counterclockwise movement and the shape of the vesicle approaches to an asymmetric
slipper shape. For this test run, the reduced area for this configuration is $\sim0.9$ which matches the previous numerical tests in \cite{Kaoui09} where a slipper-like shape occurs when the flow velocity is weak and the reduced area is large. 
A schematic of the setup is shown in Figure~\ref{figure7} where the blue horizontal line represents the mean
$y$-position of all particles. The inset of Figure~\ref{figure7} shows the trajectory of the mean position in 
$y$-direction which decreases toward $y=1$ for a period of time and starts to have an oscillatory motion.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$. The configuration is the state when $t=\{0, 4000, 8000\}$. Red curves are midplanes of three configurations. 
  }
    \label{figure6}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{Schematic of a Janus-vesicle under a parabolic flow where the strength of the flow $v_{max}=32.8$ nm ns$^{-1}$, $R_0 = 20$ nm,  and the control parameter $w=10$. The configuration is generated when $t=10000$. The inset plots the trajectory of mean $y$-position over the time.
  }
    \label{figure7}
\end{figure}

@@

With the choice of a large shear rate, a pore formation or a complete membrane rupture can be captured during simulations. Figure~\ref{figure8} shows a demonstration of a vesicle under a shear flow with shear rate $\chi=0.1$. An interesting phenomenon occurs in panels (c) and (d) where two separated bilayers move along the background shear flow symmetrically. Consequently, a periodic motion for bilayers may occur 
with the choices of shear rates. One can expect that these two layers will flow far apart from each other for much higher shear rates.

\begin{figure}
\centering
\includegraphics[height=2in]{N58_rupt_0.pdf}
\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2in]{N58_rupt_400.pdf}
\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\chi = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure8}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{Trajectories of two-vesicle in a shear flow. The moving paths of two centroids of two Janus-vesicles are plotted in blue and red. Both starting centroids of two Janus-vesicles are on the $x$-axis. 
For simulation time, $t = {0, 400,800,1200}$ for (a)-(d) and $t = {1600, 2400, 3200, 4000}$ for (e)-(h).}
    \label{figure9}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure10}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Flow}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{intro}Introduction}
Described by de Gennes as ``another animal in soft matter physics", the
Janus particle (often a spherical particle with a hydrophobic and a
hydrophilic hemisphere) exhibits complex aggregate, clustering, and
self-assembly into mesoscopic and macroscopic structures that are
relevant to a wide range of applications in biology and bioengineering.
Whether it is surface chemistry or polarity under an external field, the
dynamics of Janus particles is inevitably the combination of long-range
hydrodynamics interactions in the presence of short- and
intermediate-range particle-particle interactions. Recently~\cite{Fu20}
illustrated that the hydrophobic interactions between Janus particles in
a viscous solvent can be used as a coarse-grained model to capture the
mechanics of an elastic bilayer membrane of amphiphilic macromolecules
such as lipids. Depending on the total number of Janus particles and
their geometry, in a viscous solvent, Janus particles can aggregate to
form a micelle, a patch of bilayer membrane with open ends, and a
self-enclosed bilayer membrane (referred to as a Janus-vesicle). Using a
hybrid continuum model for the interactions between amphiphilic
particles in a viscous solvent and with a boundary integral
formulation,~\cite{Fu20} showed that the membrane granularity during
fusion and fission of bilayers can be accurately captured. 
%This boundary integral formulation has inspired more recent work

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Shear Flow}
\label{sec:ves_in_shear}
We begin by studying the dynamics of a single Janus-vesicle suspended in
the shear flow
\begin{align}
  \uu_{\infty}(\xx) = \dot\gamma (\xx \cdot \mathbf{e}_y) \mathbf{e}_x,
\end{align}
with shear rate $\dot\gamma$, and orthogonal unit vectors $\mathbf{e}_x$
and $\mathbf{e}_y$ for the horizontal and vertical directions,
respectively. It is well known that a vesicle has tank-treading behavior
when there is no viscosity contrast between the fluids inside and
outside of the vesicle.
%Within the framework of the simulation setup,
%the proposed model provides a feature that the fluid viscosity is
%constant over the computational domain and it is capable of performing
%these simulations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Intermonolayer Friction}
The granulated Janus-vesicle allows us to consider inter-monolayer slip
between two leaflets. When the shear rate is sufficiently large, take
$\chi = 0.005$ as an example, Figure~\ref{figure5} shows slip between a
pair of particles over time. The pair we consider are colored in blue
and yellow. In this series of tests, we compute the mean particle
position and mean angle $\theta(t)$ between the particle relative
positions with respect to the vesicle center. It is clear that the outer
leaflet has larger tangential velocity than the inner leaflet since the
mean angle $\theta(t)$ increases. This inter-leaflet sliding phenomenon
is consistent with what has been seen in articles in molecular dynamics
simulations.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{Slip.eps}
\includegraphics[width=0.4\textwidth]{Slip2.eps}
\end{center} 
  \caption{\label{figure5} The schematic of the intermonolayer slip over
  time. Taking a shear rate $\chi=0.005$ as an example, we denote the
  mean angle between each particle pair $\theta(t)$ where the angle is
  calculated from the relative position of the particles with respect to
  the Janus-vesicle's center of mass. The configuration plots have two
  fixed particles marked in yellow and blue and labeled with the
  corresponding time $t=2000$ and $t=9000$. The midplane curve is
  denoted as $\Sigma_M$. We see that the intermonolayer slip is largest
  at larger shear rates.}
\end{figure}

To calculate the inter-monolayer friction coefficient for the apposing
JP leaflets, we let
\begin{align}
  b = \frac{\langle F\rangle}{\langle L \rangle \langle U\rangle},
\end{align}
%
where $\langle F\rangle = \langle \int_{\mathcal{C}_M} \jump{\ttau \cdot
\sigma \cdot \nnu} \,ds\rangle$ is the time-averaged, tangential force
along the midplane curve $\mathcal{C}_m$. The parameters $\langle
L\rangle$ and $\langle U\rangle$ are the time-averaged midplane curve
length and intermonolayer slip velocity respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Vesicle in a Parabolic Flow}
Another interesting flow to consider is the parabolic flow
\begin{align}
  \uu_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2
    \right]\mathbf{e}_x,
\end{align}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the
flow. $R_0$ is defined as the radius of the Janus-vesicle at $t=0$.
The behavior of a vesicle in this unbounded non-linear flow includes
vertical migration, and depending on the flow rate and reduced area,
the steady-state shape can be either an symmetric parachute or
an asymmetric slipper~\cite{Kaoui09, cou-kao-pod-mis2008,
dan-vla-mis2009}.

%Besides the tests of a Janus-vesicle in a shear flow, an interesting
%test can also use the proposed model and the setup. Consider a
%symmetric parabolic flow about the $x$-axis,~\cite{Kaoui09} studied
%shapes of the red blood cell immersed in a parabolic flow using a
%continuum model. With a similar setup, the background flow for this set
%of simulations is given by

Figure~\ref{figure6} shows three configurations for one specific case
where the centroid of the Janus-vesicle is initially placed slightly
above the $x$-axis. The parameters are $v_{max} = 8.0$, $w=10$, and
$R_0=8$. The red curves are the midplanes and a particle pair is marked
in color. We observe that the deformed Janus-vesicle has a
counterclockwise movement and the shape of the vesicle approaches an
asymmetric slipper shape. For this test, the reduced area for this
configuration is approximately $0.9$ which matches the previous
numerical tests in~\cite{Kaoui09} where a slipper-like shape occurs when
the flow velocity is weak and the reduced area is large. A schematic of
the setup is shown in Figure~\ref{figure7} where the blue horizontal
line represents the mean $y$-position of all particles. The inset of
Figure~\ref{figure7} shows the trajectory of the mean position in the
$y$-direction which decreases toward $y=1$ for a period of time and then
starts to have an oscillatory motion due to the granularity of the
Janus-vesicle.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A Janus-vesicle suspended in a parabolic flow
  where the strength of the flow is $v_{max}=32.8$~nm ns$^{-1}$, $R_0 =
  20$~nm, and the control parameter is $w=25$~nm. The configuration is
  the state when $t=\{0, 4000, 8000\}$. The red curves are the
  midplanes.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{\label{figure7} The schematic of a Janus-vesicle suspended in
  a parabolic flow where the strength of the flow is $v_{max}=32.8$~nm
  ns$^{-1}$, $R_0 = 20$~nm, and the control parameter is $w=25$~nm. The
  configuration is generated when $t=10000$. The inset plots the
  trajectory of mean $y$-position over the time.}
\end{figure}

@@

With the choice of a large shear rate, a pore formation or a complete
membrane rupture can occur. Figure~\ref{figure8} demonstrates how a
vesicle under a shear flow with shear rate $\chi=0.1$ can rupture. The
streamlines are included in these plots. An interesting phenomenon
occurs in panels (c) and (d) where two separated bilayers move along the
background shear flow symmetrically.  Consequently, a periodic motion
for bilayers may occur with the choices of shear rates. One can expect
that these two layers will flow far apart from each other for much
higher shear rates.

\begin{figure}
\centering
\includegraphics[height=2in]{N58_rupt_0.pdf}
\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2in]{N58_rupt_400.pdf}
\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Membrane rupture occurs when the shear rate
  exceeds a threshold. Here the shear rate is $\chi = 0.1$.  Starting
  with a circular shape (panel (a)), the vesicle is stretched by the
  background flow and multiple pores appear (panel (b)).  Panels
  (c)--(d) show the later states during the simulation. Streamlines are
  included in each panel.}
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  Janus-vesicles in a shear flow. The moving paths of the two centroids
  are plotted in blue and red. The centroids are initially located on
  the $x$-axis. For simulation time, $t = {0, 400,800,1200}$ for
  (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{\label{figure10} Two Janus-vesicles under a shear flow where
  the dimensioneless shear rate is $\chi=0.005$. The initial
  configuration is shown in panel (a). The background color is the
  magnitude of fluid pressure. The color bar is identical for all
  panels. Streamlines are plotted in purple. The insets of all panels
  are generated from simulations of a continuum model of the vesicle and
  the streamlines agree between the two models.}
\end{figure}

\todo[inline]{Bryan left off here}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Flow}
